### 2013-11-07 proposal/proposal/chapter2.tex
changes

        \subsection{Definition}\label{sec:CWSDefinition}
        Community in dictionary definition refers to "the condition of sharing or having certain attitudes and interests in common" or "a group of people living in the same place or having a particular characteristic in common". In \cite{DBLP:journals/internet/BenatallahSD03, Zeng:2003:QDW:775152.775211} introduce community of web services as collection of cooperative web services with a common service and functionality but different QoS metrics. Therefore $communities$ are differentiated from $composition$ type of web service cooperation in which web services with different functionalities work together to generate a new service provider with composite functionality.

        \subsection{Architecture}\label{sec:CWSArchitecture}

        \subsection{Operations}\label{sec:CWSOperations}

            \subsubsection{Community Development}\label{sec:CWSCommunityDev}

            \subsubsection{Web Service Attraction and Retention}\label{sec:CWSAttraction}

            \subsubsection{Web Service Selection}\label{sec:CWSSelection}

        \subsection{Related Work}\label{sec:BRRelatedWork}

@@

@@

    \section{Cooperative Game Theory in Multiagent Systems}\label{sec:CGTMS}

        One the closest examples of cooperative situations, for our service model is \emph{Single landowner and landless workers} example. 
        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.

        \subsection{Related Work}\label{sec:CGTMSRelatedWork}

>>>>

        \subsection{Web Service Communities}\label{sec:CWSDefinition}
        Community in dictionary definition refers to "the condition of sharing or having certain attitudes and interests in common" or "a group of people living in the same place or having a particular characteristic in common". In \cite{DBLP:journals/internet/BenatallahSD03, Zeng:2003:QDW:775152.775211} introduce community of web services as collection of cooperative web services with a common service and functionality but different QoS metrics. Therefore $communities$ are differentiated from $composition$ type of web service cooperation in which web services with different functionalities work together to generate a new service provider with composite functionality.

        Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09} proposed the an architecture
        utilizing \emph{Contract-Net} protocol for engineering community of web services.
        This architecture has been further developed in \cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11, CSTintercommunity}.
        Community of web services have two major roles for members of a community, the master and slave web service.
        Master web services lead communities and are responsible for community and membership management of the community, they try to invite and and convince web services to join the
        community. They can attract new web services to their communities by awarding them more payoff. They also can eject some web services from the community improving the
        community and individual member satisfaction, and overall community reputation.

        \begin{figure}
            \begin{center}
            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
            \end{center}
        \end{figure}

        Figure \ref{wsarch} depicts the basic architecture of communities of web services. The main components of the architecture are: 1) the providers of web services,
        2) UDDI registries and 3) communities of web services. Communities abstract the same model of defining, announcing and invoking of web services. They also adopt the same protocols that standard web services use with UDDI registries. UDDI is a platform-independent XML based registry list which facilitates worldwide web service discovery.

        The master web service is responsible with communication with web service providers and discovery registries. It it responsible for task distribution, web service selection,
        community management, maintaining a healthy set of web services satisfying end users requests with high QoS. In communities, the masters web services can be
        dedicated web services playing the master role during the entire time of being in the community. This master web service is independently developed and never
        participates in any composition. The master web services can also be chosen out of normal web services already inside the community \cite{DBLP:journals/ijebr/MaamarSTBB09}.

    \section{Cooperative Game Theory in Multi-agent Systems}\label{sec:CGTMS}

        An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.

    \section{Related Work}\label{sec:BRRelatedWork}

@@

        Medjahed and Boubuettaya \cite{journals/dpd/MedjahedB05} have proposed a framework and a community builder mechanism which uses semantic analysis, providing an ontological organization of web services having same domain of interest. The community builder would suggest web services having similar operations with any community to join the community, or form their own communities in case the semantic analysis cannot find any community with close enough operations and service types.

@@
